Evaluating `Graphical Perception' with CNNs

### 2018-03-31 PAPER/02_experimental_setup.tex

\noindent\textbf{Image Stimuli and Labels.} 
We create our stimuli visualizations as 100$\times$100 binary images, rasterized without interpolation. We write a parameterized stimuli generator for each elementary task. The number of possible parameter values differs per experiment, and we summarize these in Table~\ref{tab:encoding_parameters} and Section~\ref{sec:parametrizations}. Before use, we scale the generated images into an unbiased range: images to the range of $-0.5$ to $0.5$. Then, we add subtle random noise (uniformly distributed between $0-0.05$) to each pixel to introduce variation which prevents the networks from simply `remembering' each different image.

@@

\subsection{Measures and Analysis}

\noindent\textbf{Cross Validation.} For reproducibility, we perform repeated random sub-sampling validation, also known as Monte Carlo cross-validation, during our experiments. We run every experiment seperately twelve times, and randomly select (without replacement) the $60\%$ of our data as training data, $20\%$ as validation, and $20\%$ as test. 
%Our large data sample size of 100,000 guarantees that every single observation of our parameterizations will be selected at least once (excluding noise patterns). -> JT: No it doesn't.
% Finally, we average the results over the runs. -> JT: Fine, but we'll do distributions anyway, so not worth saying.
\\~\\
\noindent{\textbf{Task Accuracy.}} In their 1984 paper, Cleveland and McGill use the midmean logistic absolute error metric (\emph{MLAE}) to measure perception accuracy. To allow comparison between their human results and our machine results, we also use MLAE as a presentation metric:
\begin{equation}
	\textnormal{MLAE} = log_2( | \textnormal{predicted percent} - \textnormal{true percent} | + .125)
\end{equation}
In addition to this metric, we also calculate standard error metrics such as the mean squared error (\emph{MSE}) and the mean absolute error (\emph{MAE}). This allows a more direct comparison of percent errors. Please note that our networks were trained using MSE loss and not directly with MLAE.
\\~\\
\noindent{\textbf{Task Confidence Intervals.}} We follow Cleveland and McGill and present $95\%$ confidence intervals. We approximate the value of the $97.5$ percentile point of the normal distribution for simplicity with $1.96$ as suggested by the central limit theorem~\cite{central_limit}.
\\~\\
\noindent{\textbf{Confirmatory Data Analysis.}} To accept or reject our hypotheses, we analyze dependent variables using analysis of variance (ANOVA) followed by parametric tests. JT: Which tests?
\\~\\
\noindent{\textbf{Training Efficiency.}} We use the training convergence rate as a measure of how easy or hard a particular task is for the network to learn to solve. This is defined as the MSE loss decrease per training epoch, which is an indicator of the training efficiency of the network with respect to the visual encoding.
\\~\\
\noindent\textbf{Network Generalizability.} We evaluate generalizability by asking a network previously trained upon one task parameterization to answer questions about the same type of task stimuli but with more complex parameterization, e.g., estimating bar length without and with changes in stroke width.

>>>>

\noindent\textbf{Image Stimuli and Labels.} 
We create our stimuli visualizations as 100$\times$100 binary images, rasterized without interpolation. We write a parameterized stimuli generator for each elementary task. The number of possible parameter values differs per experiment, and we summarize these in Table~\ref{tab:encoding_parameters} and Section~\ref{sec:parametrizations}. Before use, we scale the generated images into an unbiased range: images to the range of $-0.5$ to $0.5$. Then, we add subtle random noise (uniformly distributed between $-0.025$--$0.025$) to each pixel to introduce variation which prevents the networks from simply `remembering' each different image.

@@

\subsection{Measures and Analysis}
\label{sec:measuresandanalysis}

\noindent\textbf{Cross Validation.} For reproducibility, we perform repeated random sub-sampling validation, also known as Monte Carlo cross-validation, during our experiments. We run every experiment seperately twelve times, and randomly select (without replacement) the $60\%$ of our data as training data, $20\%$ as validation, and $20\%$ as test. 
%Our large data sample size of 100,000 guarantees that every single observation of our parameterizations will be selected at least once (excluding noise patterns). -> JT: No it doesn't.
% Finally, we average the results over the runs. -> JT: Fine, but we'll do distributions anyway, so not worth saying.
\\~\\
\noindent{\textbf{Task Accuracy.}} In their 1984 paper, Cleveland and McGill use the midmean logistic absolute error metric (\emph{MLAE}) to measure perception accuracy. To allow comparison between their human results and our machine results, we also use MLAE as a presentation metric:
\begin{equation}
	\textnormal{MLAE} = log_2( | \textnormal{predicted percent} - \textnormal{true percent} | + .125)
\end{equation}
In addition to this metric, we also calculate standard error metrics such as the mean squared error (\emph{MSE}) and the mean absolute error (\emph{MAE}). This allows a more direct comparison of percent errors. Please note that our networks were trained using MSE loss and not directly with MLAE.
\\~\\
\noindent{\textbf{Task Confidence Intervals.}} We follow Cleveland and McGill and present $95\%$ confidence intervals. We approximate the value of the $97.5$ percentile point of the normal distribution for simplicity with $1.96$ as suggested by the central limit theorem~\cite{central_limit}.
\\~\\
\noindent{\textbf{Confirmatory Data Analysis.}} To accept or reject our hypotheses, we analyze dependent variables using analysis of variance (ANOVA) followed by parametric tests. JT: Which tests?
\\~\\
\noindent{\textbf{Training Efficiency.}} We use the training convergence rate as a measure of how easy or hard a particular task is for the network to learn to solve. This is defined as the MSE loss decrease per training epoch, which is an indicator of the training efficiency of the network with respect to the visual encoding.
\\~\\
\noindent\textbf{Network Generalizability.} With sufficient capacity of trainable parameters, it is often said that a network can `memorize' the images if the data set has a low variability, and so it is important to consider this variability when evaluating different networks with fixed numbers of trainable parameters (Table~\ref{tab:parameters}). As discussed, we add noise to each stimulus image to prevent this. We also evaluate generalizability by asking a network previously trained upon one task parameterization to answer questions about the same type of task stimuli but with more complex parameterization, e.g., estimating bar length without and with changes in stroke width.

### 2018-03-31 PAPER/03_elementary_perceptual_tasks.tex

Cleveland and McGill describe the mapping of graphical elements to quantitative variables as \emph{elementary perceptual tasks} and introduce a list of ten different encodings in their paper~\cite{cleveland_mcgill,cleveland1985graphical}. These tasks are the low-level building blocks for information visualizations and encode quantities. Cleveland and McGill did not explicitly test human perception of single instances of these encodings. However, we test how each classifier measures encoded values using the elementary perceptual tasks and create visualizations of these tasks as rasterized images with different parametrizations (Table~\ref{tab:encoding_parameters}).

\subsection{Parametrizations}
\label{sec:parametrizations}
We generate multiple parameterizations for each elementary perceptual task and sequentially increase the number of parameters (Table~\ref{tab:encoding_parameters}). For instance, for \emph{Position Common Scale} we first only vary the $y$-position which yields just $60$ different parameters. We then include translation along the x-axis with a significant increase in variability. We then also add a variable spot size. This results in more complex datasets depending on the increase of variability. Table~\ref{tab:encoding_parameters} shows the different settings. It is important to consider this variability when evaluating different classifiers with individual trainable parameters (Table~\ref{tab:parameters}). In theory, classifiers can memorize the images if the data set has a low variability. We also counteract such behavior by adding noise.

@@

\begin{table}[!ht]
\centering
\caption{\textbf{Elementary Perceptual Tasks.} Rasterized visualizations of the elementary perceptual tasks as defined by Cleveland and McGill~\cite{cleveland_mcgill} (color saturation excluded). We sequentially increase the number of parameters (e.g. by adding translation) for every task. This introduces variability and creates increasingly more complex datasets.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lllr}
	\toprule
	\multicolumn{2}{l}{Elementary Perceptual Task} & ~ & Permutations\\
	\midrule
	\raisebox{-.85\height}{\includegraphics[width=.5in]{position_common_scale.pdf}} & \makecell[tl]{\emph{Position Common Scale}\\~~~Position Y\\~~~+ Position X \\~~~+ Spot Size \\} &~& \makecell[tr]{~\\ $60$ \\ $3,600$ \\ $216,00$}\\

@@

We proposed four hypotheses entering the elementary perceptual task experiment:

\begin{itemize}
	\item \textbf{H1.1} \textbf{Our convolutional neural networks are able to regress quantitative variables from graphical elements.} We parametrize different visual encodings (Table~\ref{tab:encoding_parameters}) and test whether the CNNs can measure them with an accuracy similar to humans.
	\item \textbf{H1.2} \textbf{Computed perceptual performance is dependent on network architexture.} We evaluate multiple regressors with different numbers of trainable parameters. A more complex network (with a higher number of parameters) might perform better on elementary perceptual tasks.
	\item \textbf{H1.3} \textbf{Some visual encodings are better than others for computations.} Cleveland and McGill order the elementary perceptual tasks by accuracy. We investigate whether this order is also relevant for computing graphical perception.
	\item \textbf{H1.4} \textbf{Networks trained on perceptual tasks can generalize to more or less complex variations of the same task.} Recent research suggests that convolutional neural networks are able to generalize by interpolating between different datapoints. While the underlying reasons are mainly yet unknown, this property allows them to perform on variations of a similar perceptual task. We create visual representations of the elementary perceptual tasks with different variability (Table~\ref{tab:encoding_parameters}). We suspect that such variations are not a problem for successfully regressing the quantitative variables and that the networks are able to generalize.
\end{itemize}

@@

The results of the elementary perceptual tasks experiment demonstrates that our networks are able to measure visually encoded quantities using low-level building blocks (Fig.~\ref{tab:figure1_results}). While the performance varies for the different encodings, we observe for all networks performance similar to the measured human performance by Cleveland and McGill~\cite{cleveland1985graphical}. These results confirm our initial hypotheses.
\\~\\
\noindent{\textbf{Accuracy.}} We report the average error across all tasks for our networks as \textit{MLAE}: 
$2.943$ ($SD=0.857$) for the multilayer perceptron, 
for LeNet $2.125$ ($SD=0.38$), 
VGG19 on ImageNet $0.979$ ($SD=0.581$), 
for VGG19 trained from scratch $0.404$ ($SD=0.407$), 
Xception on ImageNet $1.627$ ($SD=0.462$), 
and for the re-trained Xception $1.504$ ($SD=0.493$). The average error for all classifiers is \textit{MLAE}$=1.597$ ($SD=0.394$) and \textit{MAE}=$2.89$ ($SD=0.848$). VGG19 trained from scratch reaches the best performance overall.
These values are in the same ballpark as the range of $8-14\%$ error (approx. MLAE=$3$) for a similar experiment by Cleveland and McGill testing human estimation of relations between elementary perceptual tasks~\cite{cleveland1985graphical}. We therefor carefully confirm that our networks are able to regress the graphical elements to quantities within a reasonable range of error and \textbf{accept H1.1}.
\\~\\
\noindent{\textbf{Regressor Complexity.}} The performance varies not only across different visual encodings but also very much across the different network architectures. We compare the average regression performances for our networks and report the effect of the regressor as statistical significant ($F_{5,48}=20.392,p<0.01$). Post hoc comparisons show that the differences between LeNet and the VGG19 network, independent of the used weights, are significant ($t_48=4.674,p<0.01$). VGG19 from scratch and Xception (both versions) are significant, from scratch ($t_48=4.87,p<0.01$) and for imagenet weights($t_48=5.621,p<0.01$). However, differences between LeNet and both Xception networks are not significant. In any case, the variation of results also visually inspectable in Fig.~\ref{fig:figure1_results} shows the variation of performance of the different networks. We therefor \textbf{partially accept H1.2}.
\\~\\
\noindent{\textbf{Ranking of Visual Encodings.}} Cleveland and McGill provide an ordering of elementary visual encodings based on theoretical arguments and experimental results. We re-create their ranking with MLAE values of our networks in Table~\ref{tab:ranking}. The rankings differ between the different networks and Cleveland and McGill's version. However, the ranking between networks using imagenet weights is identical. Since such a ranking see,s to heavily depend on the used regressor, the weights, and the initialization, we do not think a generalized ranking can be created and \textbf{reject H1.3}.

\begin{table}[!ht]
\centering
\caption{\textbf{Ranking of Elementary Perceptual Tasks.} We create a ranking of the elementary perceptual tasks for all of our networks. We report midmean logistic absolute errors (MLAE) for each network averaged across multiple runs on the most complex parametrization of the individual stimuli. The VGG19 network performs best compared on all tasks. For human performance, we report the ranking of Cleveland and McGill~\cite{cleveland_mcgill}. The VGG19 * and Xception * networks use ImageNet weights and yield identical rankings.}
\resizebox{\linewidth}{!}{
\begin{tabular}{cllllll}
\toprule
Human & MLP & LeNet & VGG19 * & \textbf{VGG19} & Xception * & Xception \\
\midrule
\multicolumn{7}{l}{\emph{Position Common Scale}} \\
1. & 7. (3.84) & 2. (1.36) & 5. (1.02) & \textbf{3.} (-0.04) & 5. (1.65) & 1. (1.04)\\
\multicolumn{7}{l}{\emph{Position Non aligned Scale}} \\
2. & 6. (3.61) & 1. (1.35) & 6. (1.09) & \textbf{5.} (0.26) & 6. (1.71) & 2. (1.06)\\
\multicolumn{7}{l}{\emph{Length}} \\
3. & 1. (1.99) & 8. (3.19) & 4. (0.87) & \textbf{2.} (-0.14) & 4. (1.59) & 3. (1.11) \\
\multicolumn{7}{l}{\emph{Direction}} \\
3. & 9. (4.65) & 7. (3.07) & 9. (2.84) & \textbf{8.} (0.92) & 9. (3.46) & 6. (1.57) \\
\multicolumn{7}{l}{\emph{Angle}} \\
3. & 8. (4.61) & 9. (3.33) & 8. (2.31) & \textbf{9.} (0.99) & 8. (2.60) & 7. (1.72) \\
\multicolumn{7}{l}{\emph{Area}} \\
4. & 2. (2.01) & 5. (2.21) & 1. (0.49) & \textbf{1.} (-0.17) & 1. (0.80) & 5. (1.38) \\
\multicolumn{7}{l}{\emph{Volume}} \\
5. & 4. (2.38) & 4. (1.91) & 7. (1.16) & \textbf{7.} (0.87) & 7. (2.03) & 9. (2.10) \\
\multicolumn{7}{l}{\emph{Curvature}} \\
5. & 3. (2.34) & 3. (1.81) & 2. (0.71) & \textbf{6.} (0.28) & 2. (1.17) & 4. (1.13) \\
\multicolumn{7}{l}{\emph{Shading}} \\
6. & 5. (3.04) & 6. (2.23) & 3. (0.73) & \textbf{4.} (0.14) & 3. (1.57) & 8. (1.82) \\

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width=.8\linewidth]{figure1_slim_only_last.pdf}
%	\includegraphics[width=0.48\linewidth]{figure1_slim_right.pdf}
	\caption{\textbf{Computational results of Elementary Perceptual Tasks experiment.} Log absolute error means and 95\% confidence intervals for computed perception of different classifiers on the \emph{elementary perceptual tasks} introduced by Cleveland and McGill 1984~\cite{cleveland_mcgill}. We test the performance of a Multi-layer Perceptron (MLP), the LeNet Convolutional Neural Network, as well as feature generation using the VGG19 and Xception networks on the most complex parametrizations. The * indicates networks which use ImageNet weights. We also compare against an approximate human baseline of $9\%$ error reported by Cleveland and McGill.}
	\label{fig:figure1_results}
\end{figure}

>>>>

Cleveland and McGill describe a set of elementary graphical perceptual tasks across ten encodings, where each encodes a quantitative variable in a graphical element or visual mark~\cite{cleveland_mcgill,cleveland1985graphical}. These tasks are the low-level building blocks for information visualizations (Table~\ref{tab:encoding_parameters}): estimating position on a common scale, position on non-aligned scales, length, direction (or slope), angle, area, volume, curvature,  shading (or ink density), and color saturation. As human color perception is complex, and because Cleveland and McGill perform no experiments with it, for now we leave it for future work.

For the remaining nine tasks, we create visualizations as 100$\times$100 raster images, and test whether each of our networks is able to regress values from the images. As discussed in Section~\ref{sec:measuresandanalysis}, we generate multiple parameterizations for each elementary perceptual task to allow us to increase the number of parameters that the networks must estimate, and to measure performance as we move closer towards a general representation of visual marks. For instance, for \emph{Position Common Scale}, first we only vary the $y$-position of the spot to estimate against the scale, then we include translation along the x-axis, and then we vary the size of the spot size. These parameterizations are still simple---each increase is only slightly more complex for a human to solve---but it rapidly increases the number of possible images that the network must `learn' (Table~\ref{tab:encoding_parameters}).

JT: Write something about comparison to Cleveland and McGill's 1985 experimental encoding?

JT: Write something more intelligent about the different kinds of parameter variations.

%Cleveland and McGill did not explicitly test human perception of single instances of these encodings. -> JT: We now know this isn't true.

@@

\begin{table}[!ht]
\centering
\caption{\textbf{Elementary Perceptual Tasks.} Rasterized visualizations of the elementary perceptual tasks as defined by Cleveland and McGill~\cite{cleveland_mcgill} (color saturation excluded). We sequentially increase the number of parameters for every task (e.g., by adding translation). This introduces variability and creates increasingly more complex datasets.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lllr}
	\toprule
	\multicolumn{2}{l}{Elementary Perceptual Task} & ~ & Permutations\\
	\midrule
	\raisebox{-.85\height}{\includegraphics[width=.5in]{position_common_scale.pdf}} & \makecell[tl]{\emph{Position Common Scale}\\~~~Position Y\\~~~+ Position X \\~~~+ Spot Size \\} &~& \makecell[tr]{~\\ $60$ \\ $3,600$ \\ $216,00$}\\

@@

We state four hypotheses for the elementary perceptual task experiment:

\begin{itemize}
	\item \textbf{H1.1} \textbf{The CNNs tested will be able to regress quantitative variables from graphical elements.} We parametrize different visual encodings (Table~\ref{tab:encoding_parameters}) and test whether the CNNs can measure them, and relate the results to accuracies obtained by humans on similar tasks.
	\item \textbf{H1.2} \textbf{Computed perceptual performance is dependent on network architexture.} We evaluate multiple regressors with different numbers of trainable parameters. We expect a more complex network (with a higher number of trainable parameters) to perform better on elementary perceptual tasks.
	\item \textbf{H1.3} \textbf{Some visual encodings will be easier to learn than others for the CNNs tested.} Cleveland and McGill order the elementary perceptual tasks by accuracy. We investigate whether this order is also relevant for computing graphical perception.
	\item \textbf{H1.4} \textbf{Networks trained on perceptual tasks can generalize to more and less complex variations of the same task.} Empirical evidence suggests that CNNs are able to generalize by interpolating between different training data points. This property allows them to perform on variations of a similar perceptual task. We create visual representations of the elementary perceptual tasks with different variability, and expect that networks will be able to generalize when presented with slight task variations.
\end{itemize}

@@

%While the performance varies for the different encodings, we observe for all networks performance similar to the measured human performance by Cleveland and McGill~\cite{cleveland1985graphical}. These results confirm our initial hypotheses.
\noindent{\textbf{Overall Accuracy.}} The tested CNNs and MLP are able to regress the visually encoded quantities in most cases (Fig.~\ref{fig:figure1_results}), with average error across all classifiers and tasks as \textit{MLAE}$=1.597$ ($SD=0.394$). % and \textit{MAE}=$2.89$ ($SD=0.848$). 
These values are similar or better than the range of MLAE=$3.02$--$3.82$ ($8-14\%$ error) for a similar experiment by Cleveland and McGill testing human estimation of relations between elementary perceptual tasks~\cite{cleveland1985graphical}. From these results, we \textbf{accept H1.1}.
\\~\\
\noindent{\textbf{Comparing Networks.}} 
Across network architectures and training schemes, there is considerable difference in performance. In order of decreasing error: 
The MLP has \textit{MLAE}$=2.943$ ($SD=0.857$), 
for LeNet $2.125$ ($SD=0.38$), 
Xception trained on ImageNet $1.627$ ($SD=0.462$), 
Xception trained from scratch $1.504$ ($SD=0.493$),
VGG19 trained on ImageNet $0.979$ ($SD=0.581$), 
and VGG19 trained from scratch $0.404$ ($SD=0.407$).

Across tasks, we compare the average regression performances for our networks and report the effect of the network as statistically significant ($F_{5,48}=20.392,p<0.01$). Post hoc comparisons show that the differences between LeNet and the VGG19 network, independent of the used weights, are significant ($t_48=4.674,p<0.01$). VGG19 from scratch and Xception (both versions) perform significantly differently, with Xception from scratch ($t_48=4.87,p<0.01$) and Xception with ImageNet weights ($t_48=5.621,p<0.01$). However, differences between LeNet and both Xception networks are not significant. Taken collectively, we \textbf{partially accept H1.2}, in that more tunable parameters does not automatically infer greater performance.
\\~\\
\noindent{\textbf{Ranking of Visual Encodings.}} Cleveland and McGill provide an ordering of elementary visual encodings based on theoretical arguments and experimental results. We compare their ranking with rankings of our networks in Table~\ref{tab:ranking}. We note that the rankings between networks using ImageNet weights is identical; however, overall, there is significant variability, and we \textbf{reject H1.3}.

%Observing Figure~\ref{fig:figure1_results}, -> JT: we should do this.

%Since such a ranking see,s to heavily depend on the used regressor, the weights, and the initialization, we do not think a generalized ranking can be created and \textbf{reject H1.3}.

\begin{table}[tb]
\centering
\caption{\textbf{Ranking of Elementary Perceptual Tasks.} We create a ranking of the elementary perceptual tasks for all of our networks. We report midmean logistic absolute errors (MLAE) for each network averaged across multiple runs on the most complex parametrization of the individual stimuli. The VGG19 network performs best compared on all tasks. For human performance, we report the ranking of Cleveland and McGill~\cite{cleveland_mcgill}. The VGG19 * and Xception * networks use ImageNet weights and yield identical rankings.}
\resizebox{\linewidth}{!}{
\begin{tabular}{cllllll}
\toprule
Human (CMcG) & MLP & LeNet & VGG19 * & \textbf{VGG19} & Xception * & Xception \\
\midrule
\multicolumn{7}{l}{\emph{Position Common Scale}} \\
1. & 7. (3.84) & 2. (1.36) & 5. (1.02) & \textbf{3.} (-0.04) & 5. (1.65) & 1. (1.04)\\
\multicolumn{7}{l}{\emph{Position Non aligned Scale}} \\
2. & 6. (3.61) & 1. (1.35) & 6. (1.09) & \textbf{5.} (0.26) & 6. (1.71) & 2. (1.06)\\
\multicolumn{7}{l}{\emph{Length}} \\
3. & 1. (1.99) & 8. (3.19) & 4. (0.87) & \textbf{2.} (-0.14) & 4. (1.59) & 3. (1.11) \\
\multicolumn{7}{l}{\emph{Direction}} \\
3. & 9. (4.65) & 7. (3.07) & 9. (2.84) & \textbf{8.} (0.92) & 9. (3.46) & 6. (1.57) \\
\multicolumn{7}{l}{\emph{Angle}} \\
3. & 8. (4.61) & 9. (3.33) & 8. (2.31) & \textbf{9.} (0.99) & 8. (2.60) & 7. (1.72) \\
\multicolumn{7}{l}{\emph{Area}} \\
4. & 2. (2.01) & 5. (2.21) & 1. (0.49) & \textbf{1.} (-0.17) & 1. (0.80) & 5. (1.38) \\
\multicolumn{7}{l}{\emph{Volume}} \\
5. & 4. (2.38) & 4. (1.91) & 7. (1.16) & \textbf{7.} (0.87) & 7. (2.03) & 9. (2.10) \\
\multicolumn{7}{l}{\emph{Curvature}} \\
5. & 3. (2.34) & 3. (1.81) & 2. (0.71) & \textbf{6.} (0.28) & 2. (1.17) & 4. (1.13) \\
\multicolumn{7}{l}{\emph{Shading}} \\
6. & 5. (3.04) & 6. (2.23) & 3. (0.73) & \textbf{4.} (0.14) & 3. (1.57) & 8. (1.82) \\

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width=.8\linewidth]{figure1_slim_only_last.pdf}
%	\includegraphics[width=0.48\linewidth]{figure1_slim_right.pdf}
	\caption{\textbf{Elementary perceptual tasks results for most complex task parameterization.} \emph{Left:} Example stimuli image. \emph{Right:} MLAE and 95\% confidence intervals for different networks. The * indicates networks which use ImageNet weights up until the MLP, rather than being trained from scratch.}
	\label{fig:figure1_results}
\end{figure}
